### 2020-09-07 paper/coloringBergeGraphs.tex
Algos and KT fixes

Unfortunately, it is not known whether $\Theta(G)$ can be computed for all graphs (polynomial or not). If we could calculate $\alpha(G^k)$ for a first few values of $k$ (we will show how to do it in \cref{alg:maxStableSet}) we could have a lower bound on $\Theta(G)$. Let us now turn into search for some usable upper bound.

@@

Contrary to \Lovasz's first hope \cite{Lovasz1979} $\vartheta(G)$ does not always equal $\Theta(G)$, it is only an upper bound on it. However, these two equal in some graphs, including all perfect graphs, as is demonstrated in the \Lovasz "sandwich theorem" (\cref{thm:sandwich}).

@@

\subsection{Coloring perfect graph using ellipsoid method}
The following is based on \citetitle{Laurent2005} by \citeauthor{Laurent2005} \cite{Laurent2005}.

@@

In fact, to calculate $\chi(\overline{G})$ and $\alpha(G)$ we only need an approximated value of $\vartheta(G)$ with precision $< \frac{1}{2}$.

@@

There are at most $|V|$ maximum cardinality cliques in $G$. Adding a single clique to the list of maximum cardinality cliques requires constructing auxiliary graph for weighted maximum stable set, which is of size $O(V^2)$ and running \cref{alg:maxStableSet} on it. Therefore total running time is polynomial.

>>>>

Unfortunately, it is not known whether $\Theta(G)$ can be computed for all graphs in finite time. If we could calculate $\alpha(G^k)$ for a first few values of $k$ (we will show how to do it in \cref{alg:maxStableSet}) we could have a lower bound on $\Theta(G)$. Let us now turn into search for some usable upper bound.

@@

Contrary to \Lovasz's first hope \cite{Lovasz1979} $\vartheta(G)$ does not always equal $\Theta(G)$, it is only an upper bound on it. However, these two are equal for some graphs, including all perfect graphs, as is demonstrated in the \Lovasz "sandwich theorem" (\Cref{thm:sandwich}).

@@

\subsection{Coloring perfect graph using ellipsoid method}
\label{sec:coloringEllipsoid}
The following is based on \citetitle{Laurent2005} by \citeauthor{Laurent2005} \cite{Laurent2005}.

@@

In fact, to calculate $\chi(\overline{G})$ and $\alpha(G)$ we only need an approximated value of $\vartheta(G)$ with precision $< \frac{1}{2}$, as the former values are always integral.

@@

There are at most $|V|$ maximum cardinality cliques in $G$. Adding a single clique to the list of maximum cardinality cliques requires constructing auxiliary graph for weighted maximum stable set, which is of size $O(|V|^2)$ and running \cref{alg:maxStableSet} on it. Therefore total running time is polynomial.

### 2020-09-07 paper/definitions.tex
Algos and KT fixes

Given a graph $G = (V, E)$ and a set set $X \subseteq V$ by $G\setminus X$ we will denote a induced subgraph $G[V\setminus X]$.

@@

\begin{defn}[path]
  A \emph{path} is a graph $P$ of the form
  \[ V(P) = \{x_1, x_2, \ldots, x_l\},\quad E(P) = \{x_1x_2, x_2x_3, \ldots, x_{l-1}x_l\} \]
\end{defn}
This path $P$ is usually denoted by $x_1x_2\ldots x_l$ or $x_1 - x_2 - \ldots - x_l$. The vertices $x_1$ and $x_l$ are the \emph{endvertices} and ${l-1} = |E(P)|$ is the \emph{length} of the path P. $\{x_1, \ldots x_{l-1}\}$ is the \emph{inside} of the path $P$, denoted as $P^*$.

@@

\begin{defn}[anticomponent]
  An \emph{anticomponent} of a graph $G$ is an induced subgraph whose complement is a component in $G$.
\end{defn}

\begin{defn}[clique]
  A \emph{complete} graph or a \emph{clique} is a graph of the form $G = (V, {V \choose 2})$, that is every two vertices are connected. We will denote a clique of $n$ vertices as $K_n$.
\end{defn}

@@

\begin{defn}[Berge graph]
  \label{def:bergeGraph}
  A graph $G$ is \emph{Berge} if both $G$ and $\overline{G}$ have no odd hole.
\end{defn}

>>>>

Given a graph $G = (V, E)$ and a set $X \subseteq V$ by $G\setminus X$ we will denote a induced subgraph $G[V\setminus X]$.

@@

\begin{defn}[path]
  A \emph{path} is a graph $P$ of the form
  \[ V(P) = \{x_1, x_2, \ldots, x_l\},\quad E(P) = \{x_1x_2, x_2x_3, \ldots, x_{l-1}x_l\} \]
\end{defn}
This path $P$ is usually denoted by $x_1x_2\ldots x_l$ or $x_1 - x_2 - \ldots - x_l$. The vertices $x_1$ and $x_l$ are the \emph{endvertices} and ${l-1} = |E(P)|$ is the \emph{length} of the path P. $\{x_2, \ldots x_{l-1}\}$ is the \emph{inside} of the path $P$, denoted as $P^*$.

@@

\begin{defn}[anticomponent]
  An \emph{anticomponent} of a graph $G$ is an induced subgraph whose complement is a component in $\overline{G}$.
\end{defn}

\begin{defn}[clique]
  A \emph{complete} graph or a \emph{clique} is a graph of the form $G = (V, {V \choose 2})$, that is every two vertices are connected. We will denote a clique on $n$ vertices as $K_n$.
\end{defn}

@@

\TODO{Defs below to ch. 1}

\begin{defn}[Berge graph]
  \label{def:bergeGraph}
  A graph $G$ is \emph{Berge} if both $G$ and $\overline{G}$ have no odd hole as an induced subgraph
\end{defn}

### 2020-09-07 paper/implementation.tex
Plots heavy wip
Algos and KT fixes

\section{Berge graphs recognition}

@@

\TODO{a section?}
\TODO{CUDA background}
\TODO{moderngpu - allows us to run simple transforms}

@@

@@

Description.\\

Implementation.\\

Experiments and results.\\

>>>>

\section{Berge graphs recognition: na\"ive approach}
\TODO{rewrite to describe naive}

\section{Berge graphs recognition: polynomial algorithm}
\todo{rewrite/rearrange text below}

@@

\TODO{a section?}
\TODO{CUDA background}
\TODO{moderngpu - allows us to run simple transforms}
\TODO{Implementing get NC is tough -- we rely on set<bitset> to do the work. Maybe we could use a dynamic set from Adam's link? As a "open question"}

@@

\begin{figure}
  \centering
  \input{plots/hypercubes16to50.t.in.out.csv.lines.pgf}
  \caption{testPlot 1}
  % \label{fig:LCA_batch}
\end{figure}

@@

We used an open source CSDP \cite{csdpRepo, csdp1999} library, that implements predictor corrector variant of the semidefinite programming algorithm to calculate $\vartheta(G)$, given $G$ on the input. The CSDP library has been used in many recent publications across different fields, such as \cite{Ampountolas_2017, Adasme_2011}.

Calculating $\vartheta(G)$ is the most complicated part of the coloring algorithm. With that done by an external library, the rest of the program is a straightforward implementation of the algorithms in \cref{sec:coloringEllipsoid}. Our main goal of the implementation was to check if this method is still impractical, even on modern equipment. Let us proceed straight to experiments and results.

\subsubsection{Experiments and results}

### 2020-09-07 paper/main.tex
Work on combinatorial graphs
Algos and KT fixes

\chapter{Perfect Graph Coloring algorithm}
TODO

@@

>>>>

\chapter{Perfect Graph Coloring algorithm}
\label{ch:coloringSquareFree}
\section{Notes}

In appendix we use a slightly different notation than before, with many concepts represented by inline symbols. This is intended to reduce the length of algorithm's text and simplify its analysis.

\begin{itemize}
	\item $V(X)$ -- vertices of structure $X$. Will be written as $X$ when obvious.
	\item $a - b$, when $a$ and $b$ are nodes -- $a$ and $b$ are neighbors.
	\item $a \cdots b$, when $a$ and $b$ are nodes -- $a$ and $b$ are not neighbors.
	\item $a - X$, when $a$ is a node and $X$ is a set of nodes -- $a$ has a neighbor in $X$.
	\item $a \cdots X$, when $a$ is a node and $X$ is a set of nodes -- $a$ has a nonneighbor in $X$.
	\item $a \blacktriangleleft  X$, when $a$ is a node and $X$ is a set of nodes -- $a$ is complete to $X$.
	\item $a \ntriangleleft X$, when $a$ is a node and $X$ is a set of nodes -- $a$ is anticomplete to $X$.
	\item $X \setComplete Y$, when $X$ and $Y$ are set of nodes -- $X$ is complete to $Y$.
	\item $X \setAntiComplete Y$, when $X$ and $Y$ are set of nodes -- $X$ is anticomplete to $Y$.
	\item $[n]$  -- $\{1, \ldots, n\}$.
	\item \LGBSK -- a line-graph of a biparite subdivision of $K_4$.
	\item $a \gets b$ -- let a be equal b.
	\item $a :\in X$ -- let a be equal to any element of $X$
	\item $a \xor b$ -- $a$ xor $b$

	\item Strip $S_{uv}$ is \emph{rich} iff $S_{uv} \setminus T_{uv} \neq \emptyset$
\end{itemize}
\TODO{Introduction on unknown structures - J-strip etc etc}

\section{Algorithms}

\graphAppendix{Color Graph}
\input{coloringAppendix/algI.tex}
\clearpage

\graphAppendix{Color Good Partition}
\input{coloringAppendix/algII.tex}
\clearpage

\graphAppendix{Grow Hyperprism}
\input{coloringAppendix/algIII.tex}
\clearpage

\graphAppendix{Good Partition from an even hyperprism}
\input{coloringAppendix/algIV.tex}
\clearpage

\graphAppendix{Good Partition from odd hyperprism}
\input{coloringAppendix/algV.tex}
\clearpage

\graphAppendix{Good Partition from $J$-strip system}
\input{coloringAppendix/algVIa.tex}
\clearpage

\graphAppendix{Good Partition from a special $K_4$ strip system}
\input{coloringAppendix/algVIb.tex}
\clearpage

\graphAppendix{Find a special $K_4$ system}
\input{coloringAppendix/algVII.tex}
\clearpage

\graphAppendix{Growing a $J$-strip}
\input{coloringAppendix/algVIII.tex}
\clearpage

% \graphAppendix{LAST}
% \input{coloringAppendix/algIXa.tex}
% \clearpage

@@

\begin{figure}
	\input{tikzpictures/3dtest.tex}
	\caption{3d test}
\end{figure}
